\papertitle

### 2021-03-12 source_separation/paper/paper.tex
Change order of separation methods and results table

% -----------------------------------------------
% Template for SMC 2021
% Adapted from previous SMC paper templates
% -----------------------------------------------
\documentclass{article}
\usepackage{smc2021}
%%%%%%%%%%%%%%%%%%%%%%%% Some useful packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%% See related documentation %%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[caption=false, font=footnotesize]{subfig}% Modern replacement for subfigure package
\usepackage{paralist}% extended list environments
\usepackage[figure,table]{hypcap}% hyperref companion
% Enable for Review only, remove for Camera Ready version
\pagewiselinenumbers

@@

			\subsubsection{Non-negative Matrix Factorization} 
			Non-negative matrix factorization \cite{Cichocki_NMF} \cite{Fevotte_NMF} is an \`a priori method, which takes an input non-negative matrix, in this case a spectrogram $S$, in $\mathbb{R} ^{N\times M}$ and decomposes it into a basis matrix $A$ in $\mathbb{R}^{N\times J}$ and a component matrix $X$ in $\mathbb{R}^{J\times M}$ such that $S\approx A\times X$. We use the coordinate descent algorithm from the scikit-learn Python package based on \cite{Cichocki_NMF} with $J$ set to $4$, which selects for 4 features in the dataset. We then output 4 mono waveforms containing each isolated feature $F_i$, where $F_i=A_i\times X_i$ for $i = 1, 2, 3$, or $4$.

			\subsubsection{Open-Unmix}
			Open-Unmix~\cite{open-unmix} is an open source implementation of a deep music source separation model, based on \cite{Uhlich2017}. It is actually composed of multiple models that are trained for each instrumental target. Each of these models is trained on the specific target using the same architecture, based on a three layer bidirectional LSTM network. Open-Unmix operates on the Short Time Fourier Transform (STFT) of the input mixture, which is first standardized. It predicts the target by multiplying the output of the LSTM network with the magnitude spectrogram of the input, essentially applying a mask. Open-Unmix also uses Wiener filtering as a last processing step.

			\subsubsection{Demucs}
			The Demucs~\cite{demucs} architecture is a deep learning model for musical source separation. It takes as input the stereo mixture, and outputs 4 stereo waveforms corresponding to the four categories: vocals, bass, drums and other. Demucs is based on a convolutional encoder, a bidirectional LSTM, and a convolutional decoder. The encoder and the decoder are linked with skip U-Net connections. Both the encoder and the decoder are made of 6 blocks, each made of a combination of a convolutional layer with kernel size 8, followed by ReLU activation. Finally there is another convolution with kernel size 1, followed by gated linear units (GLU). The U-network structure allows the decoder to directly access the input signal and to transfer its phase, improving results.

			\subsubsection{Conv-TasNet}
			We also used the Conv-Tasnet\cite{tdcn} implementation of \cite{demucs}, who adapted the architecture, originally designed for speech separation at 8 kHz, for the task of music source separation. Conv-Tasnet uses  a combination of learned time-domain analysis and synthesis transforms with a time-dilated convolutional network (TDCN).
			Conv-Tasnet (TDCN) is a model based on a temporal convolutional encoder-decoder. It uses the audio waveform as input and performs a series of 1-D convolutions at different resolutions with residual connections in order to generate a pool of masks that are then applied on the embedding of the initial waveform to output the separated targets. A final 1-D convolutional layer is used as a decoder to recover the waveforms of each sub target. This type of architecture replaces RNNs in modeling sequential data, as series of dilated convolutions are a good way to capture temporal patterns.

			\subsubsection{Universal Sound Separation Conv-Tasnet}
			This version of Conv-Tasnet, called TDCN++, was improved by \cite{tdcnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcn}, and the changes only affect the masking network. More specifically, feature-wise normalization replaces global normalization, residual connection ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.

			TDCN++ presents the interesting property of having almost the same architecture as TDCN but trained with generic sounds. Thus, it should naturally be better suited for our task, and the comparison between those two models in particular can give good insights about the impact of the data used for training.

@@

	\begin{table}[t]
		\begin{center}
			\begin{tabular}{|c|c|}
				\hline
				& Average distance \\
				\hline
				Full target & 24.96 \\
				\hline
				NMF & 22.44 \\
				\hline
				Demucs & 25.11 \\
				\hline
				Open-Unmix & 24.48\\
				\hline
				TDCN & 26.44\\
				\hline
				TDCN++ & 24.38 \\
				\hline
				Ground truth & 24.19 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Average across 300 targets showing the distance between target and orchestration for various methods. ``Full target'' means no separation was performed. Lower values are better.}
		\label{tab:distances}
	\end{table}

>>>>

% -----------------------------------------------
% Template for SMC 2021
% Adapted from previous SMC paper templates
% -----------------------------------------------
\documentclass{article}
\usepackage{smc2021}
%%%%%%%%%%%%%%%%%%%%%%%% Some useful packages %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%% See related documentation %%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage[caption=false, font=footnotesize]{subfig}% Modern replacement for subfigure package
\usepackage{paralist}% extended list environments
\usepackage[figure,table]{hypcap}% hyperref companion
\usepackage{multirow}
% Enable for Review only, remove for Camera Ready version
\pagewiselinenumbers

@@

			\subsubsection{Music source separation}
			\textbf{Open-Unmix}\\
			Open-Unmix~\cite{open-unmix} is an open source implementation of a deep music source separation model, based on \cite{Uhlich2017}. It is actually composed of multiple models that are trained for each instrumental target. Each of these models is trained on the specific target using the same architecture, based on a three layer bidirectional LSTM network. Open-Unmix operates on the Short Time Fourier Transform (STFT) of the input mixture, which is first standardized. It predicts the target by multiplying the output of the LSTM network with the magnitude spectrogram of the input, essentially applying a mask. Open-Unmix also uses Wiener filtering as a last processing step.

			\textbf{Demucs}\\
			The Demucs~\cite{demucs} architecture is a deep learning model for musical source separation. It takes as input the stereo mixture, and outputs 4 stereo waveforms corresponding to the four categories: vocals, bass, drums and other. Demucs is based on a convolutional encoder, a bidirectional LSTM, and a convolutional decoder. The encoder and the decoder are linked with skip U-Net connections. Both the encoder and the decoder are made of 6 blocks, each made of a combination of a convolutional layer with kernel size 8, followed by ReLU activation. Finally there is another convolution with kernel size 1, followed by gated linear units (GLU). The U-network structure allows the decoder to directly access the input signal and to transfer its phase, improving results.

			\textbf{Conv-TasNet}\\
			We also used the Conv-Tasnet\cite{tdcn} implementation of \cite{demucs}, who adapted the architecture, originally designed for speech separation at 8 kHz, for the task of music source separation. Conv-Tasnet uses  a combination of learned time-domain analysis and synthesis transforms with a time-dilated convolutional network (TDCN).
			Conv-Tasnet (TDCN) is a model based on a temporal convolutional encoder-decoder. It uses the audio waveform as input and performs a series of 1-D convolutions at different resolutions with residual connections in order to generate a pool of masks that are then applied on the embedding of the initial waveform to output the separated targets. A final 1-D convolutional layer is used as a decoder to recover the waveforms of each sub target. This type of architecture replaces RNNs in modeling sequential data, as series of dilated convolutions are a good way to capture temporal patterns.

			\subsubsection{Universal sound separation}
			\textbf{Non-negative Matrix Factorization}\\
			Non-negative matrix factorization \cite{Cichocki_NMF} \cite{Fevotte_NMF} is an \`a priori method, which takes an input non-negative matrix, in this case a spectrogram $S$, in $\mathbb{R} ^{N\times M}$ and decomposes it into a basis matrix $A$ in $\mathbb{R}^{N\times J}$ and a component matrix $X$ in $\mathbb{R}^{J\times M}$ such that $S\approx A\times X$. We use the coordinate descent algorithm from the scikit-learn Python package based on \cite{Cichocki_NMF} with $J$ set to $4$, which selects for 4 features in the dataset. We then output 4 mono waveforms containing each isolated feature $F_i$, where $F_i=A_i\times X_i$ for $i = 1, 2, 3$, or $4$.

			\textbf{Universal Sound Separation Conv-Tasnet}\\
			This version of Conv-Tasnet, called TDCN++, was improved by \cite{tdcnpp} in order to be used for general sound separation, and not only for speech. The main architecture remains the same as in \cite{tdcn}, and the changes only affect the masking network. More specifically, feature-wise normalization replaces global normalization, residual connection ranges are extended to improve the flow of information, and learnable scale parameters are introduced to weight the outputs of each residual layer. Those modifications help the model to better extract features without drastically increasing its size.
			TDCN++ presents the interesting property of having almost the same architecture as TDCN but trained with generic sounds. Thus, it should naturally be better suited for our task, and the comparison between those two models in particular can give good insights about the impact of the data used for training.

@@

	\begin{table}[t]
		\begin{center}
			\begin{tabular}{|c|c|}
				\hline
				& Average distance \\
				\hline
				Demucs & 25.11 \\
				\hline
				Open-Unmix & 24.48\\
				\hline
				TDCN & 26.44\\
				\hline
				NMF & 22.44 \\
				\hline
				TDCN++ & 24.38 \\
				\hline
				Full target & 24.96 \\
				\hline
				Ground truth & 24.19 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Average across 300 targets showing the distance between target and orchestration for various methods. ``Full target'' means no separation was performed. Lower values are better.}
		\label{tab:distances}
	\end{table}

	\begin{table}[t]
		\begin{center}
		\begin{tabular}{|c|c|c|c|}
			\hline
			& Model & Average distance & Variance\\
			\hline
			\multirow{3}{4em}{Music source separation} & Open-Unmix & 24.48 & \\
			& Demucs & 25.11 & \\
			& TDCN & 26.44 & \\
			\hline
			\multirow{2}{4em}{Universal separation} & NMF & 22.44 & \\
			& TDCN+++ & 24.38 & \\
			\hline
			\multirow{2}{4em}{} & Full target & 24.96 & \\
			\hline
			& Ground truth & 24.19 & \\
			\hline
		\end{tabular}
		\end{center}
		\caption{Average across 300 targets showing the distance between target and orchestration for various methods. ``Full target'' means no separation was performed. Lower values are better.}
		\label{tab:test}
	\end{table}
